Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

Regarding gender grouping, both genders agree in their uses, so it seems not
relevant at all. However, when we look at the plot containing the sector differentiation,
it is interesting to note that university teaching staff are more likely to use chatbots 
for grades and FAQs compared to other tertiary education teachers.
This seems reasonable as the frequency of seeing the students
is lower at the University so, an automatic tool for grade notification for
continuous evaluation would be more helpful.
Furthermore, the high student-to-teacher
ratios that university teachers often face could be another reason why
a higher number of them are willing to use chatbots for FAQs, as this could
reduce misunderstandings and email overload from students.

>>>>

Regarding gender grouping, both genders agree in their uses, so it seems not
relevant at all. However, when we look at the plot containing the sector differentiation,
it is interesting to note that university teaching staff are more likely to use chatbots 
for grades and FAQs compared to other tertiary education teaching staff.
This seems reasonable as the frequency of seeing the students
is lower at the University so, an automatic tool for grade notification for
continuous evaluation would be more helpful.
Furthermore, the high student-to-teacher
ratios that university teachers often face could be another reason why
a higher number of them are willing to use chatbots for FAQs, as this could
reduce misunderstandings and email overload from students.
